---
title: "Project Presentation"
author: "Hannah Hon"
date: "7/10/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background

- This app is to graph the different EU stock Indices using histogram.
- The data used for this app is EuStockMarkets.
- EuStockMarkets contains the daily closing prices of major European stock indices: Germany DAX (Ibis), Switzerland SMI, France CAC, and UK FTSE. 

## Functionality
- The first sidebar contains the name of four EU index DAX, SMI, CAC, FTSE.
- The second sidebar controls the number of bins the histogram has.
- The first sidebar is a submit button.
- The mainpanel shows the histogram for each stock index

## ui.R
```{r, echo = TRUE}
library(shiny)
ui <- fluidPage(
  titlePanel("EuStockMarkets"),
  
  sidebarLayout(
    sidebarPanel(
      helpText("Plot for EuStockMarkets"),
      selectInput('index', 'EuStock Index', choices = c("DAX" = 1,"SMI" = 2,"CAC" = 3,"FTSE" = 4), selected = "DAX"),
      sliderInput('bins','Number of bins', min = 10, max = 100, value = 500),
      submitButton("Submit")
),
    mainPanel(plotOutput("plot"))
  )
  )
```
## Server.R

```{r, echo = TRUE}
server <- function(input, output) {

  output$plot <- renderPlot({
   data(EuStockMarkets)
   stocks <- as.data.frame(EuStockMarkets)
   c <- as.numeric(input$index)
   hist(stocks[,c], breaks = seq(1000, max(stocks[,c]), l = input$bins +1))
  })
}
```


